---
title: "cgMLST phylogenetic tree."
date: "`r format(Sys.time(), '%d %B, %Y')`"
author: "`r params$author`"

params:
  tree: tree.nwk
  method : nj
  data : data
  author: Eve Zeyl Fiskebeck
  

output: 
  prettydoc::html_pretty: 
  theme: cayman
  highlight: github
  author: params$author
  
---

<!-- note that the parameters above are defaults
The parameters provided while creating the report are provided by 
script run.sh at execution.
If you want to recompile the markdown file you can do that by 
modifying the text in the markdown (as a template)
and relaunching script (or copying the parameters above)
--> 

<!-- PREPARATION OF REPORT -->
```{r, setup, include=FALSE}
# knitr must be installed 
if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager", dependencies = T)
if (!requireNamespace("ggtree", quietly = TRUE)) BiocManager::install("ggtree")
if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman", dependencies = T)
library(pacman)
p_load(tidyverse, ggtree, treeio, ape, ggplot2)
# ggnewscale , Cairo
```


```{r, import tree, include=FALSE }
tree <- ape::read.tree(params$tree)

is_rooted <- 
  if (!is.rooted(tree)) {print("The tree is not rooted.")
  } else {print("The tree is rooted.")}
```

`r is_rooted`


```{r number of isolates, include=FALSE }
high_scale <- length(tree$tip.label)
```

If you have many isolates it is likely that the plot labels will not display correctly 
you will have to adjust the parameters.

You can also link metadata to annotate your tree. 

Please look at [the reference ggtree book](https://yulab-smu.top/treedata-book/)
and have a look at our [tutorials](https://nvi-documentation.readthedocs.io/en/latest/index.html).
PS: check in the github repo

```{r, tree plot, echo=FALSE}
# you will need to adapts those output, no automatic way 
# if you have many isolates use a cicular plot 
if (high_scale <= 300 ) {
  tree_plot <- 
  ggtree::ggtree(tree, 
                 layout = "rectangular", 
                 ladderize = T, 
                 lwd = .1) + 
  geom_tiplab(aes(label = label), size = 1) +
  geom_tippoint()  +
  ggtitle(paste0(params$method," cgMLST based phylogenetic tree")) +
  geom_treescale(fontsize = 1)  
} else {
  tree_plot <- 
    ggtree::ggtree(tree, 
                 layout = "circular", 
                 ladderize = T, 
                 lwd = .05) +
    geom_tiplab2(aes(label = label), size = 0.5) +
    geom_tippoint() +
    ggtitle(paste0(params$method," cgMLST based phylogenetic tree")) +
    geom_treescale(fontsize = 0.05)  
}

```

You might stubble upon warning message: eg. distance < 0. This can happen when distances are really small and eg for bayesian trees.

```{r echo=FALSE}
tree_plot
```


```{r, saving the plot, include=FALSE}
ggsave(filename = "tree_plot.png",
       plot = tree_plot, 
       units = "cm",
       dpi = 600, 
       width = 18, 
       heigh = 28,
       type = "cairo")
```


Parameters used in the analysis: 

  - tree: `r params$tree`
  - method : `r params$method`
  - data : `r str_remove(params$data, "^.*/")`
